%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer (DevOps and Cloud Applications)} % Job title
    {KLASS Engineering} % Organization
    {Singapore} % Location
    {Apr 2022 - Aug 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated the monitoring aspects for multi-cluster Kubernetes setup in VMWare Tanzu using Prometheus + Thanos, Loki, Logging-operator and Grafana to monitor metrics across clusters.}
        \item {Organized and wrote Kustomize setups to bootstrap new clusters with all the required services such as Istio, Cert-manager and Knative.}
        \item {Integrated ArgoCD and Argo Image Updater to our dev environment clusters to achieve GitOps-style continuous deployment.}
        \item {Developed Kubernetes operators using OperatorSDK to reconcile custom business-specific CRDs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps and Cloud Engineer} % Job title
    {IHS Markit / S\&P Global - Acquisition} % Organization
    {Singapore} % Location
    {Aug 2021 - Mar 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected an automated deployment rollout setup tied to Gitlab CI using a combination of t=Terraform, Cloud-init scipts and AWS Systems Manager.}
        \item {Acted as Cloud Infrastructure and Cybersecurity lead for our product line, achieving AWS Foundational Security Benchmark, PCI DSS and CIS AWS Foundations compliance standards on multiple AWS accounts.}
        \item {Reduced monthly infrastructure cost by performing capacity planning, identifying unnecessary and orphan resources and rightsizing overallocated resources therefore optimizing resource-usage ratio.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
  {Solutions Developer} % Job title
  {IHS Markit - Acquisition} % Organization
  {Singapore} % Location
  {May 2020 - Aug 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Automated  Packer in scheduled CI pipelines to provision custom hardened Amazon Machine Images (AMI) for our SaaS solution. Secured the base image with the required compliance agent daemons. Significantly reducing toil in verifying and tracking environments.}
      \item {Created Terraform modules to simplify complexity in performing deployments for in-house products.}
      \item {Responsible in maintaining runners for build pipelines. Migrated runners from Docker-swarm on bare-metal to Gitlab runners using spot instances.}
      \item {Enriched Gitlab pipelines with standardized CI templates for testing and compliance with features like code quality gates, container scans and SAST scanning.}
    \end{cvitems}
  }

%---------------------------------------------------------


%---------------------------------------------------------
  \cventry
  {Solutions Developer} % Job title
  {Catena Technologies} % Organization
  {Singapore} % Location
  {Jan 2019 - Apr 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Hands on development with Java Spring Boot with XSLT to develop a bespoke market trade data reporting solution.}
      \item {Responsible for all sysadmin-related efforts such as domain management, MX servers and bare-metal servers that host various tools such as Gitlab, SVN and OpenProject.}
      \item {Executed inventory compliance checks and vulnerability remediation/patching of bare-metal servers and critical services for acquisition.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
